---
title: "Clean Multiple Regression Code"
author: "Hayden Vega"
date: "2024-04-15"
output: html_document
---

```{r}
install.packages("ggeffects")
install.packages("DHARMa")
install.packages("sjlabelled")
install.packages("lme4")
install.packages("lme4", type = "source")
oo <- options(repos = "https://cran.r-project.org/")
install.packages("Matrix")
install.packages("lme4")
install.packages("glmmTMG")
install.packages("parameters")
options(oo)
install.packages("effects")
install.packages("MuMIn")
```

```{r}
library(janitor)
library(tidyverse)
library(ggeffects)
library(sjlabelled)
library(lme4)
library(DHARMa)
library(parameters)
library(effects)
library(MuMIn)
```



#Load in data for each trait with individual ID delimiter
```{r}
height_all <- read.csv("final_height.csv", header = TRUE, sep = ",") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-")

width_all <- read.csv("final_width.csv", header = TRUE, sep = ",") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-")

perimeter_all <- read.csv("final_perimeter.csv", header = TRUE, sep = ",") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-")

surf_all <- read.csv("final_surf.csv", header = TRUE, sep = ",") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-")

tdmc_all <- read.csv("final_tdmc.csv", header = TRUE, sep = ",") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-")

thickness_all <- read.csv("final_thickness.csv", header = TRUE, sep = ",") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-")

volume_all <- read.csv("final_volume.csv", header = TRUE, sep = ",") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-")



```

```{r visualization-objects}
# ggplot theme
theme_set(theme_bw() +
            theme(panel.grid = element_blank()))

# abline color
ref_line_col <- "grey"

# model prediction color
model_col <- "darkblue"
```


#Create multiple regression for each trait - initial & rehydrate WITH & WITHOUT species
```{r height-models}

height_reg_ir <- lmer(height_i ~ height_r * species + (1 | individual_id), data = height_all)
summary(height_reg_ir)

height_reg_ir_nospecies <- lmer(height_i ~ height_r + (1 | individual_id), data = height_all)
summary(height_reg_ir_nospecies)
```

```{r width-models}
width_reg_ir <- lmer(width_i ~ width_r * species + (1 | individual_id), data = width_all)
summary(width_reg_ir)

width_reg_ir_nospecies <- lmer(width_i ~ width_r + (1 | individual_id), data = width_all)
summary(width_reg_ir_nospecies)
```


```{r perimeter-models}
perimeter_reg_ir <- lmer(per_i ~ per_r * species + (1 | individual_id), data = perimeter_all)
summary(perimeter_reg_ir)

perimeter_reg_ir_nospecies <- lmer(per_i ~ per_r + (1 | individual_id), data = perimeter_all)
summary(perimeter_reg_ir_nospecies)
```


```{r surf-models}
surf_reg_ir <- lmer(surf_i ~ surf_r * species + (1 | individual_id), data = surf_all)
summary(surf_reg_ir)

surf_reg_ir_nospecies <- lmer(surf_i ~ surf_r + (1 | individual_id), data = surf_all)
summary(surf_reg_ir_nospecies)
```


```{r tdmc-models}
tdmc_reg_ir <- lmer(weight_i ~ weight_r * species + (1 | individual_id), data = tdmc_all)
summary(tdmc_reg_ir)

tdmc_reg_ir_nospecies <- lmer(weight_i ~ weight_r + (1 | individual_id), data = tdmc_all)
summary(tdmc_reg_ir_nospecies)

```


```{r thick-models}
thick_reg_ir <- lmer(thick_i ~ thick_r * species + (1 | individual_id), data = thickness_all)
summary(thick_reg_ir)

thick_reg_ir_nospecies <- lmer(thick_i ~ thick_r + (1 | individual_id), data = thickness_all)
summary(thick_reg_ir_nospecies)
```


```{r volume-models}
volume_reg_ir <- lmer(vol_i ~ vol_r * species + (1 | individual_id), data = volume_all)
summary(volume_reg_ir)

volume_reg_ir_nospecies <- lmer(vol_i ~ vol_r + (1 | individual_id), data = volume_all)
summary(volume_reg_ir_nospecies)
```



#Compare models using AIC;species & no species for Initial and Rehydrate
```{r height-AIC}
model.sel(height_reg_ir, height_reg_ir_nospecies)
#nospecies is better
```

```{r width-AIC}
model.sel(width_reg_ir, width_reg_ir_nospecies)
#nospecies is better
```

```{r perimeter-AIC}
model.sel(perimeter_reg_ir, perimeter_reg_ir_nospecies)
#with species is better
```

```{r surf-AIC}

model.sel(surf_reg_ir, surf_reg_ir_nospecies)
#species is better
```

```{r tdmc-AIC}
model.sel(tdmc_reg_ir, tdmc_reg_ir_nospecies)
#species is better
```

```{r thick-AIC}
model.sel(thick_reg_ir, thick_reg_ir_nospecies)
#nospecies is better, but doesn't really matter cause it's not a good predictor
```

```{r volume-AIC}
model.sel(volume_reg_ir, volume_reg_ir_nospecies)
#with species is better
```



#Calculating R^2 Values for the better models
```{r r^2-height}
MuMIn::r.squaredGLMM(height_reg_ir_nospecies)
```

```{r r^2-width}
MuMIn::r.squaredGLMM(width_reg_ir_nospecies)

```

```{r r2-perimeter}
MuMIn::r.squaredGLMM(perimeter_reg_ir)
```

```{r r2-surf}
MuMIn::r.squaredGLMM(surf_reg_ir)

```

```{r r2-tdmc}
MuMIn::r.squaredGLMM(tdmc_reg_ir)
```

```{r r2-thick}
MuMIn::r.squaredGLMM(thick_reg_ir_nospecies)
```

```{r r2-volume}
MuMIn::r.squaredGLMM(volume_reg_ir)
```



#Save rehydration predictions as an object using ggpredict (so we can plot later)
```{r rehydrate_height - predictions}
height_ir_predictions <- ggpredict(height_reg_ir_nospecies, terms = "height_r[0:45]") 

height_ir_predictions
```

```{r rehydrate_width - predictions}
width_ir_predictions <- ggpredict(width_reg_ir_nospecies, terms = "width_r[0:30]") #max width = 24

# look at the data frame
width_ir_predictions

```

```{r rehydrate_perimeter - predictions}
perimeter_ir_predictions <- ggpredict(perimeter_reg_ir, terms = "per_r[0:375]") 

perimeter_ir_predictions_species <- ggpredict(perimeter_reg_ir, terms = c("per_r", "species")) %>% 
  as_tibble() %>% 
  rename(species = group)
# look at the data frame
perimeter_ir_predictions
```

```{r rehydrate_surf - predictions}
surf_ir_predictions <- ggpredict(surf_reg_ir, terms = "surf_r[0:430]") 

surf_ir_predictions_species <- ggpredict(surf_reg_ir, terms = c("surf_r", "species")) %>% 
  as_tibble() %>% 
  rename(species = group)
# look at the data frame
surf_ir_predictions
```

```{r rehydrate_tdmc - predictions}
tdmc_ir_predictions <- ggpredict(tdmc_reg_ir, terms = "weight_r[0:29050]") 

tdmc_ir_predictions_species <- ggpredict(tdmc_reg_ir, terms = c("weight_r", "species")) %>% 
  as_tibble() %>% 
  rename(species = group)
# look at the data frame
tdmc_ir_predictions

```

```{r rehydrate_thick - prediction}
thick_ir_predictions <- ggpredict(thick_reg_ir_nospecies, terms = "thick_r[0:2]") 

# look at the data frame
thick_ir_predictions

```

```{r rehydrate_volume - prediction}
volume_ir_predictions <- ggpredict(volume_reg_ir, terms = "vol_r[0:30]") 

volume_ir_predictions_species <- ggpredict(volume_reg_ir, terms = c("vol_r", "species")) %>% 
  as_tibble() %>% 
  rename(species = group)
# look at the data frame
volume_ir_predictions

```


#Visualize the rehydrate models without species
```{r rehydrate_height - PLOT}
height_ir_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = height_all,
             aes(x = height_r,
                 y = height_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = height_ir_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = height_ir_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Rehydrate height (mm)",
       y = "Initial height (mm)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 60, by = 10), 
                     limits = c(0, 60)) +
  scale_y_continuous(breaks = seq(from = 0, to = 60, by = 10), 
                     limits = c(0, 60))

height_ir_plot
```

```{r rehydrate_width - PLOT}

width_ir_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = width_all,
             aes(x = width_r,
                 y = width_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = width_ir_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = width_ir_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Rehydrate Width (mm)",
       y = "Initial width (mm)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 30, by = 5), 
                     limits = c(0, 30)) +
  scale_y_continuous(breaks = seq(from = 0, to = 30, by = 5), 
                     limits = c(0, 30))
width_ir_plot

```

```{r rehydrate_thick - PLOT}
thick_ir_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = thickness_all,
             aes(x = thick_r,
                 y = thick_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = thick_ir_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = thick_ir_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Rehydrate thickness (mm)",
       y = "Initial thickness (mm)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 2, by = 0.25), 
                     limits = c(0, 2)) +
  scale_y_continuous(breaks = seq(from = 0, to = 2, by = 0.25), 
                     limits = c(0, 2))

thick_ir_plot
```



#Visualize rehydrate models with species interactions
```{r rehydrate_perimeter - PLOT}
perimeter_ir_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = perimeter_all,
             aes(x = per_r,
                 y = per_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = perimeter_ir_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = perimeter_ir_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Rehydrate perimeter (mm)",
       y = "Initial perimeter (mm)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 375, by = 50), 
                     limits = c(0, 375)) +
  scale_y_continuous(breaks = seq(from = 0, to = 375, by = 50), 
                     limits = c(0, 375))
perimeter_ir_plot


#SPECIES FACET

perimeter_ir_plot_species <- ggplot() +
  
  geom_point(data = perimeter_all,
             aes(x = per_r,
                 y = per_i,
                 color = species),
             alpha = 0.5,
             shape = 21) + 
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence intervals
  geom_ribbon(data = perimeter_ir_predictions_species,
            aes(x = x,
                y = predicted,
                ymin = conf.low,
                ymax = conf.high,
                fill = species,
                group = species),
            alpha = 0.2) +
  
  # plot the model predictions
  geom_line(data = perimeter_ir_predictions_species,
            aes(x = x,
                y = predicted,
                color = species,
                group = species)) +
  
  # labels
  labs(x = "Rehydrate perimeter (mm)",
       y = "Initial perimeter (mm)") +
  
  # theme
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 12)) +
  
  # facet
  facet_wrap(~ species, nrow = 2,
             scales = "free")


  perimeter_ir_species_plot
```

```{r rehydrate_surf - PLOT (species)}

surf_ir_plot_species <- ggplot() +
  
  geom_point(data = surf_all,
             aes(x = surf_r,
                 y = surf_i,
                 color = species),
             alpha = 0.5,
             shape = 21) + 
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence intervals
  geom_ribbon(data = surf_ir_predictions_species,
            aes(x = x,
                y = predicted,
                ymin = conf.low,
                ymax = conf.high,
                fill = species,
                group = species),
            alpha = 0.2) +
  
  # plot the model predictions
  geom_line(data = surf_ir_predictions_species,
            aes(x = x,
                y = predicted,
                color = species,
                group = species)) +
  
  # labels
  labs(x = "Rehydrate surface area (mm^2)",
       y = "Initial surface area (mm^2)") +
  
  # theme
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 12)) +
  
  # facet
  facet_wrap(~ species, nrow = 2,
             scales = "free")


  surf_ir_plot_species
```

```{r rehydrate_tdmc - plot - species}

tdmc_ir_plot_species <- ggplot() +
  
  geom_point(data = tdmc_all,
             aes(x = weight_r,
                 y = weight_i,
                 color = species),
             alpha = 0.5,
             shape = 21) + 
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence intervals
  geom_ribbon(data = tdmc_ir_predictions_species,
            aes(x = x,
                y = predicted,
                ymin = conf.low,
                ymax = conf.high,
                fill = species,
                group = species),
            alpha = 0.2) +
  
  # plot the model predictions
  geom_line(data = tdmc_ir_predictions_species,
            aes(x = x,
                y = predicted,
                color = species,
                group = species)) +
  
  # labels
  labs(x = "Rehydrate weight (g)",
       y = "Initial weight (g)") +
  
  # theme
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 12)) +
  
  # facet
  facet_wrap(~ species, nrow = 2,
             scales = "free")


 tdmc_ir_plot_species
```


```{r rehydrate-volume - PLOT}
volume_ir_plot_species <- ggplot() +
  
  geom_point(data = volume_all,
             aes(x = vol_r,
                 y = vol_i,
                 color = species),
             alpha = 0.5,
             shape = 21) + 
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence intervals
  geom_ribbon(data = volume_ir_predictions_species,
            aes(x = x,
                y = predicted,
                ymin = conf.low,
                ymax = conf.high,
                fill = species,
                group = species),
            alpha = 0.2) +
  
  # plot the model predictions
  geom_line(data = volume_ir_predictions_species,
            aes(x = x,
                y = predicted,
                color = species,
                group = species)) +
  
  # labels
  labs(x = "Rehydrate volume (mL)",
       y = "Initial volume (mL)") +
  
  # theme
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 12)) +
  
  # facet
  facet_wrap(~ species, nrow = 2,
             scales = "free")


  volume_ir_plot_species

```











#Visualize the linear model I & Rehydrate
```{r}
#Height

ggpredict(height_reg_ir, terms = c("height_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Width
ggpredict(width_reg_ir, terms = c("width_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Perimeter
ggpredict(perimeter_reg_ir, terms = c("per_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Surface Area
ggpredict(surf_reg_ir, terms = c("surf_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#TDMC
ggpredict(tdmc_reg_ir, terms = c("weight_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Thickness
ggpredict(thick_reg_ir, terms = c("thick_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Volume
ggpredict(volume_reg_ir, terms = c("vol_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

```




#Create multiple regression for each trait initial & herbarium
```{r}
#Height
height_reg_ih <- lmer(height_i ~ height_h * species + (1 | individual_id), data = height_all)
summary(height_reg_ih)

#Width
width_reg_ih <- lmer(width_i ~ width_h * species + (1 | individual_id), data = width_all)
summary(width_reg_ih)

#Perimeter
perimeter_reg_ih <- lmer(per_i ~ per_h * species + (1 | individual_id), data = perimeter_all)
summary(perimeter_reg_ih)

#Surface Area
surf_reg_ih <- lmer(surf_i ~ surf_h * species + (1 | individual_id), data = surf_all)
summary(surf_reg_ih)

#TDMC
tdmc_reg_ih <- lmer(weight_i ~ weight_h * species + (1 | individual_id), data = tdmc_all)
summary(tdmc_reg_ih)

#Thickness
thick_reg_ih <- lmer(thick_i ~ thick_h * species + (1 | individual_id), data = thickness_all)
summary(thick_reg_ih)

#Volume
volume_reg_ih <- lmer(vol_i ~ vol_h * species + (1 | individual_id), data = volume_all)
summary(volume_reg_ih)

```




#Visualize the linear models I & Herbarium
```{r}
#Height

ggpredict(height_reg_ih, terms = c("height_h", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "red"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "red"))

#Width
ggpredict(width_reg_ih, terms = c("width_h", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Perimeter
ggpredict(perimeter_reg_ih, terms = c("per_h", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Surface Area
ggpredict(surf_reg_ih, terms = c("surf_h", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#TDMC
ggpredict(tdmc_reg_ih, terms = c("weight_h", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Thickness
ggpredict(thick_reg_ir, terms = c("thick_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Volume
ggpredict(volume_reg_ih, terms = c("vol_h", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

```




#Summary graphs
```{r}
#Add 1:1 Line (I couldn't figure this out!)
#https://stackoverflow.com/questions/75101739/add-horizontal-line-to-an-effects-plot-with-different-intercepts-per-panel

#graphs without species lines
#Does this incorporate individual effects?
#height IR
ggpredict(height_reg_ir, terms = "height_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Width IR
ggpredict(width_reg_ir, terms ="width_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Perimeter IR
ggpredict(perimeter_reg_ir, terms = "per_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Surface Area IR
ggpredict(surf_reg_ir, terms = "surf_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#TDMC IR
ggpredict(tdmc_reg_ir, terms = "weight_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Thickness IR
ggpredict(thick_reg_ir, terms = "thick_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Volume IR
ggpredict(volume_reg_ir, terms = "vol_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#####IH GRAPHS Species not displayed

#height IH
ggpredict(height_reg_ih, terms = ("height_h")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "red"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "red"))

#Width
ggpredict(width_reg_ih, terms ="width_h") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Perimeter
ggpredict(perimeter_reg_ih, terms = "per_h") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Surface Area
ggpredict(surf_reg_ih, terms = "surf_h") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#TDMC
ggpredict(tdmc_reg_ih, terms = "weight_h") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Thickness
ggpredict(thick_reg_ir, terms = "thick_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Volume
ggpredict(volume_reg_ih, terms = "vol_h") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#graph with facet species
ggpredict(height_reg_ir, terms = c("height_r", "species")) %>% 
 plot(show_data=TRUE, facet = TRUE) +
scale_color_manual(values = c("black", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("black", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

```





