---
title: "Hayden's Herbarium Figure Play"
author: "Hayden Vega"
date: "2023-08-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
install.packages("janitor")
install.packages("tidyverse")
install.packages("devtools")
install_github("an-bui/calecopal")
install.packages("installr")
```

```{r}
library(janitor)
library(tidyverse)
library(calecopal)
```


##Load in the data for surface area and max height
```{r, echo=FALSE}
surf_area <- read.csv("surf_area - Sheet1.csv", header = TRUE, sep = ",")
max_height <- read.csv("max_height - Sheet1.csv", header = TRUE, sep = ",")
height <- read.csv("height_new - Sheet1.csv", header = TRUE, sep = ",")
tdmc <- read.csv("cleanedtdmc - Sheet1.csv", header = TRUE, sep = ",")
height_all <- read.csv("height poonew - Sheet1.csv", header = TRUE, sep = ",")

```
## Convert height from wide to long data
```{r}
height_long <- height_all %>% 
  pivot_longer(cols = 2:4, 
               names_to = "treatment", 
               values_to = "height")
View(height_long)
##Kinda shitty, but species of the specimen is in the height category

```
## Plot height by each species
```{r}
height_long %>% 
ggplot(aes(treatment, height, color = species))+ 
  geom_point()+
  geom_smooth(method = lm)
  #facet_wrap(~species)
```
# linear relationship summary
```{r}
height_lm <- lm(height_i~height_r, data = height_all)
summary(height_lm)
```
```{r}
height_lm <- lm(height_i~height_h, data = height_all)
summary(height_lm)
```

## Linearly plot the height for fresh vs herbarium for multiple species
```{r}
height_all %>% 
  ggplot(aes(height_h, height_i, color = species))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
  labs (x = "Height of Herbarium Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```
#plot height for fresh vs rehydrate for all 
```{r}
height_all %>% 
  ggplot(aes(height_r, height_i, color = species))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
  labs (x = "Height of Rehydrated Algae (mg)", 
        y = "Height of Fresh Algae (mg)")
```
#plot height for fres vs rehydrate 
```{r}
height_all %>% 
  ggplot(aes(height_r, height_i))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
  labs (x = "Height of Rehydrated Algae (mg)", 
        y = "Height of Fresh Algae (mg)")
```
#Plot height for fresh vs herb for all data
```{r}
height_all %>% 
  ggplot(aes(height_h, height_i))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
  labs (x = "Height of Herbarium Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```


## Filter for individual species 
#EGME
```{r}
height_EGME <- height_all %>% 
  filter (species == "EGME")

View(height_EGME)
```
#CC
```{r}
height_cc <- height_all %>% 
  filter (species == "CC")
View(height_cc)
```
#CO
```{r}
height_co <- height_all %>% 
  filter (species =="CO")
view(height_co)
```
#CYOS
```{r}
height_CYOS <- height_all %>% 
  filter (species == "CYOS")
View(height_CYOS)
```
#R
```{r}
height_R <- height_all %>% 
  filter (species =="R")
View(height_R)
```



#SUMMARY ALL Linear models for each species for heighti vs height h vs r



#EGME
#herb vs I
```{r}
height_EGME_lm <- lm(height_i~height_h, data = height_EGME) #apply linear model to height dataset, weight_i = y, h = x

summary(height_EGME_lm)
```
#rehydrate vs I
```{r}
height_EGME_lm_r <- lm(height_i~height_r, data = height_EGME)
summary(height_EGME_lm_r)
```
# herb vs rehydrate
```{r}
height_EGME_lm_hr <- lm(height_r~height_h, data = height_EGME)
summary(height_EGME_lm_hr)
```

#CC herb vs I
```{r}
height_cc_lm <- lm(height_i~height_h, data = height_cc) #apply linear model to height dataset, weight_i = y, h = x

summary(height_cc_lm)

```
#rehydrate vs initial
```{r}
height_cc_lm_r <- lm(height_i~height_r, data = height_cc)
summary(height_cc_lm_r)
```
#herb vs rehydrate
```{r}
height_cc_lm_hr <- lm(height_r~height_h, data = height_cc)
summary(height_cc_lm_hr)
```


#CO herb vs in
```{r}
height_co_lm <- lm(height_i~height_h, data = height_co) #apply linear model to height dataset, weight_i = y, h = x

summary(height_co_lm)
```
# re vs in
```{r}
height_co_lm_r <- lm(height_i~height_r, data = height_co)
summary(height_co_lm_r)
```
# herb vs re

```{r}
height_co_lm_hr <- lm(height_r~height_h, data = height_co)
summary(height_co_lm_hr)
```



#CYOS herb vs i
```{r}
height_CYOS_lm <- lm(height_i~height_h, data = height_CYOS) #apply linear model to height dataset, weight_i = y, h = x

summary(height_CYOS_lm)
```
# rehydrate vs i
```{r}
height_CYOS_lm_r <- lm(height_i~height_r, data = height_CYOS)
summary(height_CYOS_lm_r)
```
# i vs r
```{r}
height_CYOS_lm_hr <- lm(height_r~height_h, data = height_CYOS)
summary(height_CYOS_lm_hr)
```
#R h vs i
```{r}
height_R_lm <- lm(height_i~height_h, data = height_R) #apply linear model to height dataset, weight_i = y, h = x

summary(height_R_lm)
```
# r vs i
```{r}
height_R_lm_r <- lm(height_i~height_r, data = height_R)
summary(height_R_lm_r)
```
# herb vs re
```{r}
height_R_lm_hr <- lm(height_r~height_h, data = height_R)
summary(height_R_lm_hr)
```


# GRAPH EM ALL for height 
#EGME herb vs i
```{r}
height_EGME_lm %>% 
  ggplot(aes(height_h, height_i))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 10, y = 35, label= "y = 1.25x - 0.58
      R squared = 0.987")+ #labeling the rsquared and slope
  labs (x = "Height of Herbarium Algae (cm)", 
        y = "Height of Fresh Algae (cm)")

```
#EGME rehydrate vs i
```{r}
height_EGME %>% 
  ggplot(aes(height_r, height_i))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 10, y = 35, label= "y = 1.00x - 0.34
       R squared = 0.994")+ #labeling the rsquared and slope
  labs (x = "Height of Rehydrated Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```
#EGME herb vs rehydrate
```{r}
height_EGME %>% 
  ggplot(aes(height_h, height_r))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 10, y = 35, label= "y = 1.12x - 0.889
       R squared = 0.990")+ #labeling the rsquared and slope
  labs (x = "Height of Rehydrated Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```

#CC herb vs i
```{r}
height_cc_lm %>% 
  ggplot(aes(height_h, height_i))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 12.5, y = 35, label= "y = 0.996x - 0.73
      R squared = 0.963")+ #labeling the rsquared and slope
  labs (x = "Height of Herbarium Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```
#CC rehydrate vs i
```{r}
height_cc %>% 
  ggplot(aes(height_r, height_i))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 15, y = 35, label= "y = 0.965x + 0.725
       R squared = 0.997")+ #labeling the rsquared and slope
  labs (x = "Height of Rehydrated Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```
#CC herb vs rehydrate
```{r}
height_cc %>% 
  ggplot(aes(height_h, height_r))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 12.5, y = 35, label= "y = 1.48x - 4.35
       R squared = 0.980")+ #labeling the rsquared and slope
  labs (x = "Height of Rehydrated Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```
#CO rehydrate vs I
```{r}
height_co %>% 
  ggplot(aes(height_r, height_i))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 10, y = 35, label= "y = 0.956x - 0.533
       R squared = 0.986")+ #labeling the rsquared and slope
  labs (x = "Height of Rehydrated Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```

#CO Herb vs I
```{r}
height_co_lm %>% 
  ggplot(aes(height_h, height_i))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 5.7, y = 35, label= "y = 1.40x - 3.4
      R squared = 0.963")+ #labeling the rsquared and slope
  labs (x = "Height of Herbarium Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```
#CO herb vs rehydrate
```{r}
height_co %>% 
  ggplot(aes(height_h, height_r))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 10, y = 35, label= "y = 1.10x - 0.473
       R squared = 0.985")+ #labeling the rsquared and slope
  labs (x = "Height of Rehydrated Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```
#CYOS Herb vs I
```{r} 
height_CYOS_lm %>% 
  ggplot(aes(height_h, height_i))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 14.5, y = 35, label= "y = 1.36x - 1.54
      R squared = 0.490")+ #labeling the rsquared and slope
  labs (x = "Height of Herbarium Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```
#CYOS rehydrate vs I
```{r}
height_CYOS %>% 
  ggplot(aes(height_r, height_i))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 20, y = 35, label= "y = 1.01x - 0.412
       R squared = 0.999")+ #labeling the rsquared and slope
  labs (x = "Height of Rehydrated Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```
# CYOS herb vs rehydrate
```{r}
height_CYOS %>% 
  ggplot(aes(height_h, height_r))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 13, y = 35, label= "y = 1.34x - 1.71
       R squared = 0.4845")+ #labeling the rsquared and slope
  labs (x = "Height of Rehydrated Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```
#R Herb vs I
```{r}
height_R_lm %>% 
  ggplot(aes(height_h, height_i))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 5, y = 25, label= "y = 1.12x - 0.217
      R squared = 0.790")+ #labeling the rsquared and slope
  labs (x = "Height of Herbarium Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```

#R rehydrate vs I
```{r}
height_R %>% 
  ggplot(aes(height_r, height_i))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 10, y = 35, label= "y = 0.766x - 1.86
       R squared = 0.")+ #labeling the rsquared and slope
  labs (x = "Height of Rehydrated Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```
#R herb vs rehydrate
```{r}
height_R %>% 
  ggplot(aes(height_h, height_r))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
 annotate("text", x = 10, y = 35, label= "y = 1.16x + 0.548
       R squared = 0.780")+ #labeling the rsquared and slope
  labs (x = "Height of Rehydrated Algae (cm)", 
        y = "Height of Fresh Algae (cm)")
```


# facet for linear stuff?
```{r}
height_all %>% 
  ggplot(aes(height_h, height_i))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
# annotate("text", x = 5, y = 30, label= "y = 1.12x - 0.217
     # R squared = 0.979")+ #labeling the rsquared and slope
 # labs (x = "Height of Herbarium Algae (cm)", 
       # y = "Height of Fresh Algae (cm)")+
  facet_grid(~species)

```




## create height_long_EGME, which is the height values for only EGME specimens
```{r}
height_long_EGME <- height_long %>% 
  filter(species == "EGME")
```
#plot height for EGME using height_long_EGME dataset
```{r}
height_long_EGME %>%  
 ggplot(aes(treatment, height))+
  geom_point()
```

  ## Plot herbarium height against initial height for EGME
  ## create new herbarium vs inital dataset
```{r}
height_ih_EGME <- height_long_EGME %>% 
  filter(treatment %in% 
  c("height_i","height_h"))
```
  
  ## Filter TDMC values to get only EGME
```{r}
tdmc_EGME <- tdmc %>% 
  filter (species == "EGME")

View(tdmc_EGME)

```

##View the stats for tdmc linear model

```{r}
tdmc_EGME_lm <- lm(weight_i~weight_h, data = tdmc_EGME) #apply linear model to tdmc dataset, weight_i = y, h = x

summary(tdmc_EGME_lm)
```

  ## Plot herbarium weight against initial weight;linear model 
```{r}
tdmc_EGME_lm %>% 
  ggplot(aes(weight_h, weight_i))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = FALSE)+
  annotate("text", x = 50, y = 2500, label= "y = 7.32x + 52.1
      R squared = 0.938")+ #labeling the rsquared and slope
  labs (x = "Weight of Herbarium Algae (mg)", 
        y = "Weight of Fresh Algae (mg)")




```


  
##make data wide again bruh
```{r}
height_ih_EGME_test <- height_ih_EGME %>% 
  pivot_wider (names_from = "treatment", 
               values_from = "height")

```
## Set scale of X and Y axis to be equal = 35
```{r}
height_ih_EGME_test <- data.frame(x=rnorm(35), 
                                   y=rnorm(35))
View(height_ih_EGME_test)
```

## plot herbarium by initial for EGME
```{r}
height_ih_EGME_test %>% 
  ggplot(aes(height_i, height_h))+
  geom_point()
```


## Convert surf_area from long to wide data; Long dataset to be called surf_long

```{r pressure, echo=FALSE}
surf_long <- surf_area %>% 
  pivot_longer(cols = 2:4, 
               names_to = "treatment", 
               values_to = "area")
View(surf_long)
```

##Plot long data in linear
```{r}
ggplot(data = surf_long, 
       mapping = aes(x = treatment, 
                     y = area))+
  geom_point()
  


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
