---
title: "Multiple Regression Code"
author: "Hayden Vega"
date: "2024-02-14"
output: html_document
---
```{r}
install.packages("ggeffects")
install.packages("DHARMa")
install.packages("sjlabelled")
install.packages("lme4")
install.packages("lme4", type = "source")
oo <- options(repos = "https://cran.r-project.org/")
install.packages("Matrix")
install.packages("lme4")
install.packages("glmmTMG")
install.packages("parameters")
options(oo)
```

```{r}
library(janitor)
library(tidyverse)
library(ggeffects)
library(sjlabelled)
library(lme4)
library(DHARMa)
library(glmmTMG)
library(parameters)

#New data 2/13
thick <- read.csv("2_13 code  - thick.csv", header = TRUE, sep = ",")
width <- read.csv("2_13 code  - max_width.csv", header = TRUE, sep = ",")
height <- read.csv("2_13 code  - max_height.csv", header = TRUE, sep = ",")
height_all <- read.csv("2_13 code  - max_height.csv", header = TRUE, sep = ",") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-")
cor_set <- read.csv("2_13 code  - h,w,t.csv", header = TRUE, sep = ",")
egme_diff_ir <- read.csv("EGME Residual Calculation - max_height.csv", header = TRUE, sep = ",")
species_diff_ir <- read.csv("Residual_mult_species - max_height.csv", header = TRUE, sep = ",")

```
# cor to long data for grouping by trait
```{r}
cor_long <- cor_set %>% 
  pivot_longer(cols = 3:11, 
               names_to = "treatment", 
               values_to = "value")
View(cor_long)

```
##Filter for herbarium and fresh traits
```{r}
h_r_traits <- cor_long %>% 
filter (treatment == "width_i" | treatment == "width_h" | treatment == "height_i" | treatment == "height_h" | treatment == "avg_i" | treatment == "avg_h")
 view(h_r_traits)
```

## Predictors grouped by trait # I'm stuck
```{r}
h_r_traits %>% 
  ggplot(aes(species, value, color = "treatment"))+
  geom_point()+
  geom_smooth(formula = "y~x", method = "lm", se = TRUE)+
  labs (x = "Height of Herbarium Algae (cm)", 
        y = "Height of Fresh Algae (cm)")+
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), panel.background = element_blank())
  #facet_wrap(~species, 
            # strip.position = "top")
  

```
#Single linear regression initial and rehydrate
```{r}
height_lm <- lm(height_i~height_r, data = height_all)
summary(height_lm)

lm(formula = height_i~height_r, data = height_all)
```

#MULTIPLE REGRESSION
```{r}
height_r_mult_reg <- lm(height_i ~ height_r * species, data = height_all)

summary(height_r_mult_reg)




height_r_mul_better <- lmer(height_i ~ height_r * species + (1 | individual_id), data = height_all)
summary(height_r_mul_better)

```
#Plot the model
```{r}

library(sjlabelled)
data(efc)
fit <- lm(barthtot ~ c12hour + neg_c_7 + c161sex + c172code, data = efc)

ggpredict(height_r_mul_better, terms = c("height_r", "species")) %>% 
  plot(show_data=TRUE)+
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3"))+
  scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3"))
  

model_parameters(height_r_mul_better)



```
#create data frame from predictions
```{r}
height_predictions <- ggpredict(height_r_mul_better, terms = c("height_r", "species"))
view(height_predictions)
intercept <-  -0.296204
egme_slope <- 0.167271
r_egme <- 0.002756
predict_value <- 10.16106462

egme_slope * 10 + intercept

(egme_slope) * 10 + intercept

```

#Add individual#column
```{r}
df <- tibble(id = 1:3, x = c("m-123", "f-455", "f-123"))
view(df)
# There are three basic ways to split up a string into pieces:
# 1. with a delimiter
 #code has been input above when we load in data so we don't have to change it everytime. 
# height_all %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  # unite("individual_id", date:individual, remove = TRUE, sep = "-")


```

**Residual Modeling using Dharma**
```{r}
height_r_residuals <- simulateResiduals(fittedModel = height_r_mul_better, plot = T)
#Results suggest the relationship may be overfitted; too complex; Underdispersed

testDispersion(height_r_residuals, plot = T, type = ("DHARMa"))

testDispersion(height_r_residuals, alternative = "less", plot = T)


#I don't know what this does or how to interpret it

```

#figure out if single regression is better

```{r}
height_r_residuals_single <- simulateResiduals(fittedModel = height_lm, plot = T)

```

```{r}
plotResiduals(height_r_residiuals) # right plot in plot.DHARMa()

```
#FILTER BY EGME SPECIES
```{r}
height_EGME <- height_all %>% 
  filter (species == "EGME")

```
#Run multiple regression for single species
```{r}
height_r_mul_EGME <- lmer(height_i ~ height_r + (1 | individual_id), data = height_EGME)
summary(height_r_mul_EGME)

#height_r_mul_better <- lmer(height_i ~ height_r * species + (1 | individual_id), data = height_all)
#The species factor was removed. Should it be included? Or is it okay to have it removed because we are looking at each species separately?

```
#look at EGME RESIDUALS #use to make % error calulations easier?
```{r}
height_r_EGME_residuals <- simulateResiduals(fittedModel = height_r_mul_EGME, plot = T)
testDispersion(height_r_EGME_residuals, alternative = "less", plot = T)

```
#Use equation to calculate percent difference in sheets
#boxplot of percent error residuals _IR_EGME
```{r}

egme_diff_ir_plot <- ggplot(egme_diff_ir, aes(x=species, y = percent_difference_r))
 egme_diff_ir_plot + geom_boxplot()
  


```
#Plot residuals of multiple species
```{r}
species_diff_ir_plot <- ggplot(species_diff_ir, aes(x=species, y = percent_difference_r))
 species_diff_ir_plot + geom_boxplot()

```



