---
title: "Clean Multiple Regression Code"
author: "Hayden Vega and An Bui"
date: "2025-05-05"
output:
  word_document: default
  html_document: default
  pdf_document: default
description: This file contains code for Mixed effect models and corresponding visualizations for all traits and treatments of the Functional trait project. This is the most recent version as of 5/5/25
---

```{r}
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
##                                    Setup                                 ----
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


#.........................Install Packages.........................

install.packages("ggeffects")
install.packages("DHARMa")
install.packages("sjlabelled")
install.packages("lme4")
install.packages("lme4", type = "source")
oo <- options(repos = "https://cran.r-project.org/")
install.packages("Matrix")
install.packages("lme4")
install.packages("glmmTMG")
install.packages("parameters")
options(oo)
install.packages("effects")
install.packages("MuMIn")
install.packages("lmerTest")
#.........................Load Libraries.........................
library(janitor)
library(tidyverse)
library(ggeffects)
library(sjlabelled)
library(lme4)
library(DHARMa)
library(parameters)
library(effects)
library(MuMIn)
library(waffle)
library(showtext)
library(lmerTest)
#.........................Load Fonts.........................
font_add_google(name = "Marcellus", family = "marc")
font_add_google(name = "Josefin Sans", family = "josefin")
font_add_google(name = "Lexend", family = "lex")
#.........................Assigning a Standard ggplot Theme.........................
# ggplot theme
theme_set(theme_bw() +
            theme(panel.grid = element_blank(), 
                  plot.background = element_blank()))

# abline color
ref_line_col <- "grey"

# model prediction color
model_col <- "darkblue"

#.........................Reading in Data for all Seven Traits and Treatments.........................
       #each model has an added column (specimen) that denotes subsample

height_all <- read.csv("../data/preliminary_data/final_height.csv") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-") 

width_all <- read.csv("../data/preliminary_data/final_width.csv", header = TRUE, sep = ",") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-")

perimeter_all <- read.csv("../data/preliminary_data/final_perimeter.csv", header = TRUE, sep = ",") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-")

surf_all <- read.csv("../data/preliminary_data/final_surf.csv", header = TRUE, sep = ",") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-")

tdmc_all <- read.csv("../data/preliminary_data/final_tdmc.csv", header = TRUE, sep = ",") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-")

thickness_all <- read.csv("../data/preliminary_data/final_thickness.csv", header = TRUE, sep = ",") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-")

volume_all <- read.csv("../data/preliminary_data/final_volume.csv", header = TRUE, sep = ",") %>% separate_wider_delim(specimen_id, delim = "-", names = c("date", "site", "individual", "specimen"), cols_remove=FALSE) %>% 
  unite("individual_id", date:individual, remove = TRUE, sep = "-")

```

##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
##                      Making Mixed Effect Linear Models                   ----
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

#    Models with Rehydrated Traits as Predictor Variables     ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
     
     
```{r height-models, include=FALSE}
#..........................Height Models.........................

height_reg_ir <- lmer(height_i ~ height_r * species + (1 | individual_id), data = height_all)
summary(height_reg_ir)

#...............................................................................
#                                                                              .
#  A mixed effect model with height_i as our response variable, height_r as    .
#  our predictor variable, and species as an interaction term. individual_id   .
#  is included as a random effect.                                             .
#                                                                              .
#...............................................................................

height_reg_ir_nospecies <- lmer(height_i ~ height_r + (1 | individual_id), data = height_all)
summary(height_reg_ir_nospecies)

#...............................................................................
#                                                                              .
#  A mixed effect model with height_i as our response variable, height_r as    .
#  our predictor variable, and individual_id as a random effect.               . 
#                                                                              .
#...............................................................................
```

```{r width-models}
#..........................Width Models.........................

width_reg_ir <- lmer(width_i ~ width_r * species + (1 | individual_id), data = width_all)
summary(width_reg_ir)
#...............................................................................
#                                                                              .
#  A mixed effect model with width_i as our response variable, width_r as our  .
#  predictor, and species as an interaction term. individual_id is included    .
#  as a random effect.                                                         .
#                                                                              .
#...............................................................................

width_reg_ir_nospecies <- lmer(width_i ~ width_r + (1 | individual_id), data = width_all)
summary(width_reg_ir_nospecies)

#...............................................................................
#                                                                              .
#  A mixed effect model with width_i as our response variable, width_r as our  .
#  predictor, and individual_id as a random effect.
#                                                                              .
#                                                                              .
#...............................................................................
```

```{r perimeter-models}
#..........................Perimeter Models.........................

perimeter_reg_ir <- lmer(per_i ~ per_r * species + (1 | individual_id), data = perimeter_all)
summary(perimeter_reg_ir)
#...............................................................................
#                                                                              .
#  A mixed effect model with per_i as our response variable, per_r as our      .
#  predictor, species as an interaction term, and individual_id as a random    .
#  effect.                                                                     .
#                                                                              .
#...............................................................................

perimeter_reg_ir_nospecies <- lmer(per_i ~ per_r + (1 | individual_id), data = perimeter_all)
summary(perimeter_reg_ir_nospecies)

#...............................................................................
#                                                                              .
#  A mixed effect model with per_i as our response variable, per_r as our      .
#  predictor, and individual_id as a random effect.                            .
#                                                                              .
#...............................................................................
```


```{r surf-models}
#..........................Surface Area Models.........................

surf_reg_ir <- lmer(surf_i ~ surf_r * species + (1 | individual_id), data = surf_all)
summary(surf_reg_ir)
#...............................................................................
#                                                                              .
#  A mixed effect model with surf_i as our response variable, surf_r as our      .
#  predictor, species as an interaction term, and individual_id as a random    .
#  effect.                                                                     .
#                                                                              .
#...............................................................................

surf_reg_ir_nospecies <- lmer(surf_i ~ surf_r + (1 | individual_id), data = surf_all)
summary(surf_reg_ir_nospecies)
#...............................................................................
#                                                                              .
#  A mixed effect model with surf_i as our response variable, surf_r as our      .
#  predictor, and individual_id as a random effect.                            .
#                                                                              .
#...............................................................................
```


```{r tdmc-models}
#..........................Weight Models.........................

tdmc_reg_ir <- lmer(weight_i ~ weight_r * species + (1 | individual_id), data = tdmc_all)
summary(tdmc_reg_ir)
#...............................................................................
#                                                                              .
#  A mixed effect model with weight_i as our response variable, weight_r as our      .
#  predictor, species as an interaction term, and individual_id as a random    .
#  effect.                                                                     .
#                                                                              .
#...............................................................................

tdmc_reg_ir_nospecies <- lmer(weight_i ~ weight_r + (1 | individual_id), data = tdmc_all)
summary(tdmc_reg_ir_nospecies)
#...............................................................................
#                                                                              .
#  A mixed effect model with weight_i as our response variable, weight_r as our      .
#  predictor, and individual_id as a random effect.                            .
#                                                                              .
#...............................................................................

```

```{r thick-models}
#..........................Thickness Models.........................

thick_reg_ir <- lmer(thick_i ~ thick_r * species + (1 | individual_id), data = thickness_all)
summary(thick_reg_ir)
#...............................................................................
#                                                                              .
#  A mixed effect model with thick_i as our response variable, thick_r as our      .
#  predictor, species as an interaction term, and individual_id as a random    .
#  effect.                                                                     .
#                                                                              .
#...............................................................................

thick_reg_ir_nospecies <- lmer(thick_i ~ thick_r + (1 | individual_id), data = thickness_all)
summary(thick_reg_ir_nospecies)
#...............................................................................
#                                                                              .
#  A mixed effect model with thick_i as our response variable, thick_r as our      .
#  predictor, and individual_id as a random effect.                            .
#                                                                              .
#...............................................................................
```


```{r volume-models}
#..........................Volume Models.........................

volume_reg_ir <- lmer(vol_i ~ vol_r * species + (1 | individual_id), data = volume_all)
summary(volume_reg_ir)
#...............................................................................
#                                                                              .
#  A mixed effect model with vol_i as our response variable, vol_r as our      .
#  predictor, species as an interaction term, and individual_id as a random    .
#  effect.                                                                     .
#                                                                              .
#...............................................................................

volume_reg_ir_nospecies <- lmer(vol_i ~ vol_r + (1 | individual_id), data = volume_all)
summary(volume_reg_ir_nospecies)
#...............................................................................
#                                                                              .
#  A mixed effect model with vol_i as our response variable, vol_r as our      .
#  predictor, and individual_id as a random effect.                            .
#                                                                              .
#...............................................................................
```

#     Models with Herbarium Traits as Predictor Variables     ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
     
```{r height-herbarium-models}
#..........................Height Models.........................

height_reg_ih <- lmer(height_i ~ height_h * species + (1 | individual_id), data = height_all)
summary(height_reg_ih)
#...............................................................................
#                                                                              .
#  A mixed effect model with height_i as our response variable, height_h as our.
#  predictor, species as an interaction term, and individual_id as a random    .
#  effect.                                                                     .
#                                                                              .
#...............................................................................

height_reg_ih_nospecies <- lmer(height_i ~ height_h + (1 | individual_id), data = height_all)
summary(height_reg_ih_nospecies)
#...............................................................................
#                                                                              .
#  A mixed effect model with height_i as our response variable, height_h as our.
#  predictor, and individual_id as a random effect.                            .
#                                                                              .
#...............................................................................
```

```{r width-herbarium-models}
#..........................Width Models.........................

width_reg_ih <- lmer(width_i ~ width_h * species + (1 | individual_id), data = width_all)
summary(width_reg_ih)
#...............................................................................
#                                                                              .
#  A mixed effect model with width_i as our response variable, width_h as our.
#  predictor, species as an interaction term, and individual_id as a random    .
#  effect.                                                                     .
#                                                                              .
#...............................................................................

width_reg_ih_nospecies <- lmer(width_i ~ width_h + (1 | individual_id), data = width_all)
summary(width_reg_ih_nospecies)
#...............................................................................
#                                                                              .
#  A mixed effect model with width_i as our response variable, width_h as our  .
#  predictor, and individual_id as a random effect.                            .
#                                                                              .
#...............................................................................
```

```{r perimeter-herbarium-models}
#..........................Perimeter Models.........................

perimeter_reg_ih <- lmer(per_i ~ per_h * species + (1 | individual_id), data = perimeter_all)
summary(perimeter_reg_ih)
#...............................................................................
#                                                                              .
#  A mixed effect model with per_i as our response variable, per_h as our      .
#  predictor, species as an interaction term, and individual_id as a random    .
#  effect.                                                                     .
#                                                                              .
#...............................................................................
perimeter_reg_ih_nospecies <- lmer(per_i ~ per_h + (1 | individual_id), data = perimeter_all)
summary(perimeter_reg_ih_nospecies)
#...............................................................................
#                                                                              .
#  A mixed effect model with per_i as our response variable, per_h as our      .
#  predictor, and individual_id as a random effect.                            .
#                                                                              .
#...............................................................................
```


```{r surf-herbarium-models}
#..........................Surface Area Models.........................

surf_reg_ih <- lmer(surf_i ~ surf_h * species + (1 | individual_id), data = surf_all)
summary(surf_reg_ih)
#...............................................................................
#                                                                              .
#  A mixed effect model with surf_i as our response variable, surf_h as our    .
#  predictor, species as an interaction term, and individual_id as a random    .
#  effect.                                                                     .
#                                                                              .
#...............................................................................

surf_reg_ih_nospecies <- lmer(surf_i ~ surf_h + (1 | individual_id), data = surf_all)
summary(surf_reg_ih_nospecies)
#...............................................................................
#                                                                              .
#  A mixed effect model with surf_i as our response variable, surf_h as our    .
#  predictor, and individual_id as a random effect.                            .
#                                                                              .
#...............................................................................
```


```{r tdmc-herbarium-models}
#..........................Weight Models.........................

tdmc_reg_ih <- lmer(weight_i ~ weight_h * species + (1 | individual_id), data = tdmc_all)
summary(tdmc_reg_ih)
#...............................................................................
#                                                                              .
#  A mixed effect model with weight_i as our response variable, weight_h as our.
#  predictor, species as an interaction term, and individual_id as a random    .
#  effect.                                                                     .
#                                                                              .
#...............................................................................
tdmc_reg_ih_nospecies <- lmer(weight_i ~ weight_h + (1 | individual_id), data = tdmc_all)
summary(tdmc_reg_ih_nospecies)
#...............................................................................
#                                                                              .
#  A mixed effect model with weight_i as our response variable, weight_h as our.
#  predictor, and individual_id as a random effect.                            .
#                                                                              .
#...............................................................................
```

```{r thick-herbarium-models}
#..........................Thickness Models.........................

thick_reg_ih <- lmer(thick_i ~ thick_h * species + (1 | individual_id), data = thickness_all)
summary(thick_reg_ih)
#...............................................................................
#                                                                              .
#  A mixed effect model with thick_i as our response variable, thick_h as our  .
#  predictor, species as an interaction term, and individual_id as a random    .
#  effect.                                                                     .
#                                                                              .
#...............................................................................
thick_reg_ih_nospecies <- lmer(thick_i ~ thick_h + (1 | individual_id), data = thickness_all)
summary(thick_reg_ih_nospecies)
#...............................................................................
#                                                                              .
#  A mixed effect model with thick_i as our response variable, thick_h as our  .
#  predictor, and individual_id as a random effect.                            .
#                                                                              .
#...............................................................................
```


```{r volume-herbarium-models}
#..........................Volume Models.........................

volume_reg_ih <- lmer(vol_i ~ vol_h * species + (1 | individual_id), data = volume_all)
summary(volume_reg_ih)
#...............................................................................
#                                                                              .
#  A mixed effect model with vol_i as our response variable, vol_h as our    .
#  predictor, species as an interaction term, and individual_id as a random    .
#  effect.                                                                     .
#                                                                              .
#...............................................................................
volume_reg_ih_nospecies <- lmer(vol_i ~ vol_h + (1 | individual_id), data = volume_all)
summary(volume_reg_ih_nospecies)
#...............................................................................
#                                                                              .
#  A mixed effect model with vol_i as our response variable, vol_h as our      .
#  predictor, and individual_id as a random effect.                            .
#                                                                              .
#...............................................................................
```

##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
##                         Comparing Models using AIC                       ----
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

     # Comparisons for Models With Rehydrated Traits as Predictor Variables ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r height-AIC}
#..........................Comparisons for Height Models........................

model.sel(height_reg_ir, height_reg_ir_nospecies)
#nospecies is better
```

```{r width-AIC}
#..........................Comparisons for Width Models.........................

model.sel(width_reg_ir, width_reg_ir_nospecies)
#nospecies is better
```

```{r perimeter-AIC}
#..........................Comparisons for Perimeter Models......................

model.sel(perimeter_reg_ir, perimeter_reg_ir_nospecies)
#with species is better
```

```{r surf-AIC}
#..........................Comparisons for Surface Area Models..................

model.sel(surf_reg_ir, surf_reg_ir_nospecies)
#species is better
```

```{r tdmc-AIC}
#..........................Comparisons for Weight Models........................

model.sel(tdmc_reg_ir, tdmc_reg_ir_nospecies)
#species is better
```

```{r thick-AIC}
#..........................Comparisons for Thickness Models.....................

model.sel(thick_reg_ir, thick_reg_ir_nospecies)
#nospecies is better, but rehydrated thickness it's not a good predictor overall
```

```{r volume-AIC}
#..........................Comparisons for Volume Models........................

model.sel(volume_reg_ir, volume_reg_ir_nospecies)
#with species is better
```

     # AIC Comparisons for Models With Herbarium Traits as Predictor Variables ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
     
```{r height-herbarium-AIC}
#..........................Comparisons for Height Models........................

model.sel(height_reg_ih, height_reg_ih_nospecies)
#nospecies is better
```

```{r width-herbarium-AIC}
#..........................Comparisons for Width Models........................

model.sel(width_reg_ih, width_reg_ih_nospecies)
#species is better
```

```{r perimeter-herbarium-AIC}
#.......................Comparisons for Perimeter Models........................

model.sel(perimeter_reg_ih, perimeter_reg_ih_nospecies)
#with species is better
```

```{r surf-herbarium-AIC}
#....................Comparisons for Surface Area Models........................

model.sel(surf_reg_ih, surf_reg_ih_nospecies)
#species is better
```

```{r tdmc-herbarium-AIC}
#..........................Comparisons for Weight Models........................

model.sel(tdmc_reg_ih, tdmc_reg_ih_nospecies)
#species is better
```

```{r thick-herbarium-AIC}
#.......................Comparisons for Thickness Models........................

model.sel(thick_reg_ih, thick_reg_ih_nospecies)
#species is better, but doesn't really matter cause it's not a good predictor
```

```{r volume-herbarium-AIC}
#..........................Comparisons for Volume Models........................

model.sel(volume_reg_ih, volume_reg_ih_nospecies)
#with species is better
```

##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## Calculating R Squared Values for the Best Fitting Models From Each Trait and Treatment---
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

     # R Values for Models with Rehydrated Traits as Predictor Variables ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r r^2-height}
#..................R^2 for Height Model without species interaction term........

MuMIn::r.squaredGLMM(height_reg_ir_nospecies)

```

```{r r^2-width}
#..................R^2 for Width Model without species interaction term........

MuMIn::r.squaredGLMM(width_reg_ir_nospecies)

```

```{r r2-perimeter}
#...............R^2 for Perimeter Model with species interaction term........

MuMIn::r.squaredGLMM(perimeter_reg_ir)
```

```{r r2-surf}
#............R^2 for Surface Area Model with species interaction term........

MuMIn::r.squaredGLMM(surf_reg_ir)

```

```{r r2-tdmc}
#..................R^2 for Weight Model with species interaction term........

MuMIn::r.squaredGLMM(tdmc_reg_ir)
```

```{r r2-thick}
#...............R^2 for Thickness Model without species interaction term........

MuMIn::r.squaredGLMM(thick_reg_ir_nospecies)
```

```{r r2-volume}
#..................R^2 for Volume Model with species interaction term........

MuMIn::r.squaredGLMM(volume_reg_ir)
```

     # R Values for Models with Herbarium Traits as Predictor Variables ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
     
```{r r^2-herbarium-height}
#..................R^2 for Height Model without species interaction term........

MuMIn::r.squaredGLMM(height_reg_ih_nospecies)
```

```{r r^2-herbarium-width}
#..................R^2 for Width Model with species interaction term............

MuMIn::r.squaredGLMM(width_reg_ih)

```

```{r r2-herbarium-perimeter}
#...............R^2 for Perimeter Model with species interaction term........

MuMIn::r.squaredGLMM(perimeter_reg_ih)
```

```{r r2-herbarium-surf}
#............R^2 for Surface Area Model with species interaction term........

MuMIn::r.squaredGLMM(surf_reg_ih)

```

```{r r2-herbarium-tdmc}
#..................R^2 for Weight Model with species interaction term........

MuMIn::r.squaredGLMM(tdmc_reg_ih)
```

```{r r2-herbarium-thick}
#..................R^2 for Thickness Model with species interaction term........

MuMIn::r.squaredGLMM(thick_reg_ih)
```

```{r r2-herbarium-volume}
#..................R^2 for Volume Model with species interaction term...........

MuMIn::r.squaredGLMM(volume_reg_ih)
```

     

##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
##        Saving Model Predictions as Objects for Later Visualization       ----
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

     # Predictions for Models with Rehydrated Traits as Predictor Variables ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r rehydrate_height - predictions}
     #........Predictions for the Height Model Without Species........

height_ir_predictions <- ggpredict(height_reg_ir_nospecies, terms = "height_r[0:45]") %>% 
  mutate(trait = "height")

height_ir_predictions
```

```{r rehydrate_width - predictions}
     #........Predictions for the Width Model Without Species........

width_ir_predictions <- ggpredict(width_reg_ir_nospecies, terms = "width_r[0:30]") %>% #max width = 24
  mutate(trait = "width") 

# look at the data frame
width_ir_predictions

```

```{r rehydrate_perimeter - predictions}
     #........Predictions for the Height Model With Species........
perimeter_ir_predictions <- ggpredict(perimeter_reg_ir, terms = "per_r[0:375]") %>% 
  mutate(trait = "perimeter")

     #...........Incorporating Species as a Prediction Term...........
perimeter_ir_predictions_species <- ggpredict(perimeter_reg_ir, terms = c("per_r", "species")) %>% 
  as_tibble() %>% #converting to a tibble
  rename(species = group)
# look at the data frame
perimeter_ir_predictions
```

```{r rehydrate_surf - predictions}
     #........Predictions for the Height Model With Species........

surf_ir_predictions <- ggpredict(surf_reg_ir, terms = "surf_r[0:430]") %>% 
  mutate(trait = "surface area")

     #...........Incorporating Species as a Prediction Term...........
surf_ir_predictions_species <- ggpredict(surf_reg_ir, terms = c("surf_r", "species")) %>% 
  as_tibble() %>% 
  rename(species = group)
# look at the data frame
surf_ir_predictions
```

```{r rehydrate_tdmc - predictions fig.width = 20, fig.height = 10}
     #........Predictions for the Weight Model With Species........

tdmc_ir_predictions <- ggpredict(tdmc_reg_ir, terms = "weight_r[0:29050]") %>% 
  as_tibble() %>% 
  mutate(trait = "thallus dry matter content")

     #...........Incorporating Species as a Prediction Term...........
tdmc_ir_predictions_species <- ggpredict(tdmc_reg_ir, terms = c("weight_r", "species")) %>% 
  as_tibble() %>% 
  rename(species = group)
# look at the data frame
tdmc_ir_predictions

```

```{r rehydrate_thick - prediction}
     #........Predictions for the Thickness Model Without Species........

thick_ir_predictions <- ggpredict(thick_reg_ir_nospecies, terms = "thick_r[0:2]")  %>% 
  mutate(trait = "thickness")

# look at the data frame
thick_ir_predictions

```

```{r rehydrate_volume - prediction}
     #........Predictions for the Volume Model With Species........

volume_ir_predictions <- ggpredict(volume_reg_ir, terms = "vol_r[0:30]") %>% 
  mutate(trait = "volume")

     #...........Incorporating Species as a Prediction Term...........
volume_ir_predictions_species <- ggpredict(volume_reg_ir, terms = c("vol_r", "species")) %>% 
  as_tibble() %>% 
  rename(species = group)
# look at the data frame
volume_ir_predictions

```

     # Predictions for Models with Herbarium Traits as Predictor Variables ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
     
```{r height-herbarium - predictions}

     #........Predictions for the Height Model Without Species........
height_ih_predictions <- ggpredict(height_reg_ih_nospecies, terms = "height_h[0:45]") 

height_ih_predictions
```

```{r width-herbarium - predictions}
    
 #........Predictions for the Width Model Without Species........
width_ih_predictions <- ggpredict(width_reg_ih_nospecies, terms = "width_h[0:30]") #max width = 24

# look at the data frame
width_ih_predictions

     #...........Incorporating Species as a Prediction Term...........
width_ih_predictions_species <- ggpredict(width_reg_ih, terms = c("width_h", "species")) %>% 
  as_tibble() %>% 
  rename(species = group)


```

```{r perimeter-herbarium - predictions}
     
#........Predictions for the Perimeter Model With Species........
perimeter_ih_predictions <- ggpredict(perimeter_reg_ih, terms = "per_h[0:375]") 

     #...........Incorporating Species as a Prediction Term...........
perimeter_ih_predictions_species <- ggpredict(perimeter_reg_ih, terms = c("per_h", "species")) %>% 
  as_tibble() %>% 
  rename(species = group)
# look at the data frame
perimeter_ih_predictions_species
```

```{r surf-herbarium - predictions}
   
 #........Predictions for the Surface Area Model With Species........
surf_ih_predictions <- ggpredict(surf_reg_ih, terms = "surf_h[0:430]") 

     #...........Incorporating Species as a Prediction Term...........
surf_ih_predictions_species <- ggpredict(surf_reg_ih, terms = c("surf_h", "species")) %>% 
  as_tibble() %>% 
  rename(species = group)
# look at the data frame
surf_ih_predictions_species
```

```{r tdmc-herbarium - predictions}

     #........Predictions for the Weight Model With Species........

tdmc_ih_predictions <- ggpredict(tdmc_reg_ih, terms = "weight_h[0:29050]") 

     #...........Incorporating Species as a Prediction Term...........
tdmc_ih_predictions_species <- ggpredict(tdmc_reg_ih, terms = c("weight_h", "species")) %>% 
  as_tibble() %>% 
  rename(species = group)
# look at the data frame
tdmc_ih_predictions
tdmc_ih_predictions_species

```

```{r thick-herbarium - prediction}
     #........Predictions for the Thickness Model Without Species........

thick_ih_predictions <- ggpredict(thick_reg_ih_nospecies, terms = "thick_h[0:2]") 

# look at the data frame
thick_ih_predictions

     #...........Incorporating Species as a Prediction Term...........
thick_ih_predictions_species <- ggpredict(thick_reg_ih, terms = c("thick_h", "species"))  %>% 
  as_tibble() %>% 
  rename(species = group)

```

```{r volume-herbarium - prediction}

     #........Predictions for the Volume Model With Species........
volume_ih_predictions <- ggpredict(volume_reg_ih, terms = "vol_h[0:30]") 

     #...........Incorporating Species as a Prediction Term...........
volume_ih_predictions_species <- ggpredict(volume_reg_ih, terms = c("vol_h", "species")) %>% 
  as_tibble() %>% 
  rename(species = group)
# look at the data frame
volume_ih_predictions
volume_ih_predictions_species

```
     
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
##                             Visualizing Models                           ----
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

     #        Visualizing Rehydrate Models Without Species         ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r rehydrate_height - PLOT}

     #.....Scatterplot of height_r(x) as Predictor of height_i(y).....

height_ir_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = height_all,
             aes(x = height_r,
                 y = height_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = height_ir_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = height_ir_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Rehydrate height (mm)",
       y = "Initial height (mm)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 50, by = 10), 
                     limits = c(0, 50)) +
  scale_y_continuous(breaks = seq(from = 0, to = 50, by = 10), 
                     limits = c(0, 50))+
  #add equation + r squared
   annotate("text", x = 10, y = 45, label= "y = 1.02x + 0.0407
R squared = 0.996")
  

height_ir_plot
```

```{r rehydrate_width - PLOT}

     #.....Scatterplot of width_r(x) as Predictor of width_i(y).....

width_ir_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = width_all,
             aes(x = width_r,
                 y = width_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = width_ir_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = width_ir_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Rehydrate Width (mm)",
       y = "Initial width (mm)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 30, by = 5), 
                     limits = c(0, 30)) +
  scale_y_continuous(breaks = seq(from = 0, to = 30, by = 5), 
                     limits = c(0, 30))+
  #add equation + r squared
   annotate("text", x = 10, y = 25, label= "y = 0.994x + 0.0865
R squared = 0.996")
  
width_ir_plot

```

```{r rehydrate_thick - PLOT fig.width = 20, fig.height = 10}
     
     #.....Scatterplot of thickness_r(x) as Predictor of thickness_i(y).....

thick_ir_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = thickness_all,
             aes(x = thick_r,
                 y = thick_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = thick_ir_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = thick_ir_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Rehydrate thickness (mm)",
       y = "Initial thickness (mm)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 2, by = 0.25), 
                     limits = c(0, 2)) +
  scale_y_continuous(breaks = seq(from = 0, to = 2, by = 0.25), 
                     limits = c(0, 2))+
  #add equation + r squared
   annotate("text", x = 0.75, y = 1.75, label= "y = 0.922x + 0.134
R squared = 0.882")

thick_ir_plot
```

     #          Visualizing Rehydrate Models With Species          ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r rehydrate_perimeter - PLOT}
     #.....Scatterplot of perimeter_r(x) as Predictor of perimeter_i(y).....
perimeter_ir_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = perimeter_all,
             aes(x = per_r,
                 y = per_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = perimeter_ir_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = perimeter_ir_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Rehydrate perimeter (mm)",
       y = "Initial perimeter (mm)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 375, by = 50), 
                     limits = c(0, 375)) +
  scale_y_continuous(breaks = seq(from = 0, to = 375, by = 50), 
                     limits = c(0, 375))+
  #add equation + r squared
   annotate("text", x = 75, y = 300, label= "y = 1.02x + 0.0407
R squared = 0.996")
perimeter_ir_plot

  #.Scatterplot of height_r(x) as Predictor of height_i(y) with a species facet.

perimeter_ir_plot_species <- ggplot() +
  
  geom_point(data = perimeter_all,
             aes(x = per_r,
                 y = per_i,
                 color = species),
             alpha = 0.5,
             shape = 21) + 
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence intervals
  geom_ribbon(data = perimeter_ir_predictions_species,
            aes(x = x,
                y = predicted,
                ymin = conf.low,
                ymax = conf.high,
                fill = species,
                group = species),
            alpha = 0.2) +
  
  # plot the model predictions
  geom_line(data = perimeter_ir_predictions_species,
            aes(x = x,
                y = predicted,
                color = species,
                group = species)) +
  
  # labels
  labs(x = "Rehydrate perimeter (mm)",
       y = "Initial perimeter (mm)") +
  
  # theme
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 12)) +
  
  # facet
  facet_wrap(~ species, nrow = 2,
             scales = "free")


  perimeter_ir_plot_species
```

```{r rehydrate_surf - PLOT (species)}

     #.....Scatterplot of surf_r(x) as Predictor of surf_i(y).....

surf_ir_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = surf_all,
             aes(x = surf_r,
                 y = surf_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = surf_ir_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = surf_ir_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Rehydrate Surface Area (mm^2)",
       y = "Initial Surface Area (mm^2)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 450, by = 75), 
                     limits = c(0, 450)) +
  scale_y_continuous(breaks = seq(from = 0, to = 450, by = 75), 
                     limits = c(0, 450))
surf_ir_plot

 #.Scatterplot of surf_r(x) as Predictor of surf_i(y) with a species facet.
surf_ir_plot_species <- ggplot() +
  
  geom_point(data = surf_all,
             aes(x = surf_r,
                 y = surf_i,
                 color = species),
             alpha = 0.5,
             shape = 21) + 
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence intervals
  geom_ribbon(data = surf_ir_predictions_species,
            aes(x = x,
                y = predicted,
                ymin = conf.low,
                ymax = conf.high,
                fill = species,
                group = species),
            alpha = 0.2) +
  
  # plot the model predictions
  geom_line(data = surf_ir_predictions_species,
            aes(x = x,
                y = predicted,
                color = species,
                group = species)) +
  
  # labels
  labs(x = "Rehydrate surface area (mm^2)",
       y = "Initial surface area (mm^2)") +
  
  # theme
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 12)) +
  
  # facet
  facet_wrap(~ species, nrow = 2,
             scales = "free")


  surf_ir_plot_species
```

```{r rehydrate_tdmc - plot - species}
    
 #.....Scatterplot of weight_r(x) as Predictor of weight_i(y).....

tdmc_ir_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = tdmc_all,
             aes(x = weight_r,
                 y = weight_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = tdmc_ir_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = tdmc_ir_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Rehydrate weight (g)",
       y = "Initial weight (g)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 4850, by = 810), 
                     limits = c(0, 4850)) +
  scale_y_continuous(breaks = seq(from = 0, to = 4850, by = 810), 
                     limits = c(0, 4850))
tdmc_ir_plot

  #.Scatterplot of weight_r(x) as Predictor of weight_i(y) with a species facet.


tdmc_ir_plot_species <- ggplot() +
  
  geom_point(data = tdmc_all,
             aes(x = weight_r,
                 y = weight_i,
                 color = species),
             alpha = 0.5,
             shape = 21) + 
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence intervals
  geom_ribbon(data = tdmc_ir_predictions_species,
            aes(x = x,
                y = predicted,
                ymin = conf.low,
                ymax = conf.high,
                fill = species,
                group = species),
            alpha = 0.2) +
  
  # plot the model predictions
  geom_line(data = tdmc_ir_predictions_species,
            aes(x = x,
                y = predicted,
                color = species,
                group = species)) +
  
  # labels
  labs(x = "Rehydrate weight (g)",
       y = "Initial weight (g)") +
  
  # theme
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 12)) +
  
  # facet
  facet_wrap(~ species, nrow = 2,
             scales = "free")


 tdmc_ir_plot_species
```

```{r rehydrate-volume - PLOT}
     
#.....Scatterplot of vol_r(x) as Predictor of vol_i(y).....

volume_ir_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = volume_all,
             aes(x = vol_r,
                 y = vol_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = volume_ir_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = volume_ir_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Rehydrate volume (mL)",
       y = "Initial volume (mL)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 15, by = 2.5), 
                     limits = c(0, 15)) +
  scale_y_continuous(breaks = seq(from = 0, to = 15, by = 2.5), 
                     limits = c(0, 15))
volume_ir_plot

  #.Scatterplot of volume_r(x) as Predictor of volume_i(y) with a species facet.


volume_ir_plot_species <- ggplot() +
  
  geom_point(data = volume_all,
             aes(x = vol_r,
                 y = vol_i,
                 color = species),
             alpha = 0.5,
             shape = 21) + 
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence intervals
  geom_ribbon(data = volume_ir_predictions_species,
            aes(x = x,
                y = predicted,
                ymin = conf.low,
                ymax = conf.high,
                fill = species,
                group = species),
            alpha = 0.2) +
  
  # plot the model predictions
  geom_line(data = volume_ir_predictions_species,
            aes(x = x,
                y = predicted,
                color = species,
                group = species)) +
  
  # labels
  labs(x = "Rehydrate volume (mL)",
       y = "Initial volume (mL)") +
  
  # theme
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 12)) +
  
  # facet
  facet_wrap(~ species, nrow = 2,
             scales = "free")


  volume_ir_plot_species

```

     #        Visualizing Herbarium Models Without Species         ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
     
```{r height-herbarium - PLOT}

     #....Scatterplot of height_h(x) as a Predictor of height_i(y)....
height_ih_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = height_all,
             aes(x = height_h,
                 y = height_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = height_ih_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = height_ih_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Herbarium height (mm)",
       y = "Initial height (mm)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 50, by = 10), 
                     limits = c(0, 50)) +
  scale_y_continuous(breaks = seq(from = 0, to = 50, by = 10), 
                     limits = c(0, 50))+
  #add equation + r squared
   annotate("text", x = 10, y = 45, label= "y = 1.14x + 0.258
R squared = 0.929")

height_ih_plot
```

     #           Visualize HERBARIUM models with species           ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r width-herbarium - PLOT}
    
 #....Scatterplot of width_h(x) as a Predictor of width_i(y)....
width_ih_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = width_all,
             aes(x = width_h,
                 y = width_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = width_ih_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = width_ih_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Herbarium width (mm)",
       y = "Initial width (mm)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 20, by = 5), 
                     limits = c(0, 20)) +
  scale_y_continuous(breaks = seq(from = 0, to = 20, by = 5), 
                     limits = c(0, 20))
width_ih_plot

  #.Scatterplot of width_h(x) as Predictor of width_i(y) with a species facet.
width_ih_plot_species <- ggplot() +
  
  geom_point(data = width_all,
             aes(x = width_h,
                 y = width_i,
                 color = species),
             alpha = 0.5,
             shape = 21) + 
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence intervals
  geom_ribbon(data = width_ih_predictions_species,
            aes(x = x,
                y = predicted,
                ymin = conf.low,
                ymax = conf.high,
                fill = species,
                group = species),
            alpha = 0.2) +
  
  # plot the model predictions
  geom_line(data = width_ih_predictions_species,
            aes(x = x,
                y = predicted,
                color = species,
                group = species)) +
  
  # labels
  labs(x = "Herbarium width (mm)",
       y = "Initial width (mm)") +
  
  # theme
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 12)) +
  
  # facet
  facet_wrap(~ species, nrow = 2,
             scales = "free")


  width_ih_plot_species

```

```{r thick-herbarium - PLOT}

     #....Scatterplot of thick_h(x) as a Predictor of thick_i(y)....
thick_ih_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = thickness_all,
             aes(x = thick_h,
                 y = thick_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = thick_ih_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = thick_ih_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Rehydrate thickness (mm)",
       y = "Initial thickness (mm)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 2, by = 0.25), 
                     limits = c(0, 2)) +
  scale_y_continuous(breaks = seq(from = 0, to = 2, by = 0.25), 
                     limits = c(0, 2))

thick_ih_plot

  #.Scatterplot of thick_h(x) as Predictor of thick_i(y) with a species facet.
thick_ih_plot_species <- ggplot() +
  
  geom_point(data = thickness_all,
             aes(x = thick_h,
                 y = thick_i,
                 color = species),
             alpha = 0.5,
             shape = 21) + 
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence intervals
  geom_ribbon(data = thick_ih_predictions_species,
            aes(x = x,
                y = predicted,
                ymin = conf.low,
                ymax = conf.high,
                fill = species,
                group = species),
            alpha = 0.2) +
  
  # plot the model predictions
  geom_line(data = thick_ih_predictions_species,
            aes(x = x,
                y = predicted,
                color = species,
                group = species)) +
  
  # labels
  labs(x = "Herbarium thickness (mm)",
       y = "Initial thickness (mm)") +
  
  # theme
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 12)) +
  
  # facet
  facet_wrap(~ species, nrow = 2,
             scales = "free")


  thick_ih_plot_species

```

```{r perimeter-herbarium - PLOT}

     #....Scatterplot of per_h(x) as a Predictor of per_i(y)....
perimeter_ih_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = perimeter_all,
             aes(x = per_h,
                 y = per_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = perimeter_ih_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = perimeter_ih_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Herbarium perimeter (mm)",
       y = "Initial perimeter (mm)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 375, by = 50), 
                     limits = c(0, 375)) +
  scale_y_continuous(breaks = seq(from = 0, to = 375, by = 50), 
                     limits = c(0, 375))
perimeter_ih_plot


  #.Scatterplot of per_h(x) as Predictor of per_i(y) with a species facet.
perimeter_ih_plot_species <- ggplot() +
  
  geom_point(data = perimeter_all,
             aes(x = per_h,
                 y = per_i,
                 color = species),
             alpha = 0.5,
             shape = 21) + 
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence intervals
  geom_ribbon(data = perimeter_ih_predictions_species,
            aes(x = x,
                y = predicted,
                ymin = conf.low,
                ymax = conf.high,
                fill = species,
                group = species),
            alpha = 0.2) +
  
  # plot the model predictions
  geom_line(data = perimeter_ih_predictions_species,
            aes(x = x,
                y = predicted,
                color = species,
                group = species)) +
  
  # labels
  labs(x = "Herbarium perimeter (mm)",
       y = "Initial perimeter (mm)") +
  
  # theme
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 12)) +
  
  # facet
  facet_wrap(~ species, nrow = 2,
             scales = "free")


  perimeter_ih_plot_species
```

```{r surf-herbarium - PLOT (species)}

     #....Scatterplot of surf_h(x) as a Predictor of surf_i(y)....
surf_ih_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = surf_all,
             aes(x = surf_h,
                 y = surf_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = surf_ih_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = surf_ih_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Herbarium Surface Area (mm^2)",
       y = "Initial Surface Area (mm^2)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 450, by = 75), 
                     limits = c(0, 450)) +
  scale_y_continuous(breaks = seq(from = 0, to = 450, by = 75), 
                     limits = c(0, 450))
surf_ih_plot

  #.Scatterplot of surf_h(x) as Predictor of surf_i(y) with a species facet.
surf_ih_plot_species <- ggplot() +
  
  geom_point(data = surf_all,
             aes(x = surf_r,
                 y = surf_i,
                 color = species),
             alpha = 0.5,
             shape = 21) + 
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence intervals
  geom_ribbon(data = surf_ih_predictions_species,
            aes(x = x,
                y = predicted,
                ymin = conf.low,
                ymax = conf.high,
                fill = species,
                group = species),
            alpha = 0.2) +
  
  # plot the model predictions
  geom_line(data = surf_ih_predictions_species,
            aes(x = x,
                y = predicted,
                color = species,
                group = species)) +
  
  # labels
  labs(x = "Herbarium Surface Area (mm^2)",
       y = "Initial Surface Area (mm^2)") +
  
  # theme
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 12)) +
  
  # facet
  facet_wrap(~ species, nrow = 2,
             scales = "free")


  surf_ih_plot_species
```

```{r tdmc-herbarium - plot - species}

     #....Scatterplot of weight_h(x) as a Predictor of weight_i(y)....
tdmc_ih_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = tdmc_all,
             aes(x = weight_h,
                 y = weight_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = tdmc_ih_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = tdmc_ih_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Herbarium weight (g)",
       y = "Initial weight (g)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 4850, by = 810), 
                     limits = c(0, 4850)) +
  scale_y_continuous(breaks = seq(from = 0, to = 4850, by = 810), 
                     limits = c(0, 4850))
tdmc_ih_plot


  #.Scatterplot of weight_h(x) as Predictor of weight_i(y) with a species facet.
tdmc_ih_plot_species <- ggplot() +
  
  geom_point(data = tdmc_all,
             aes(x = weight_h,
                 y = weight_i,
                 color = species),
             alpha = 0.5,
             shape = 21) + 
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence intervals
  geom_ribbon(data = tdmc_ih_predictions_species,
            aes(x = x,
                y = predicted,
                ymin = conf.low,
                ymax = conf.high,
                fill = species,
                group = species),
            alpha = 0.2) +
  
  # plot the model predictions
  geom_line(data = tdmc_ih_predictions_species,
            aes(x = x,
                y = predicted,
                color = species,
                group = species)) +
  
  # labels
  labs(x = "Herbarium weight (g)",
       y = "Initial weight (g)") +
  
  # theme
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 12)) +
  
  # facet
  facet_wrap(~ species, nrow = 2,
             scales = "free")


 tdmc_ih_plot_species
```

```{r volume-herbarium - PLOT}

     #....Scatterplot of vol_h(x) as a Predictor of vol_i(y)....
volume_ih_plot <- ggplot() +
  
  # plot the raw data as points
  geom_point(data = volume_all,
             aes(x = vol_h,
                 y = vol_i),
             alpha = 0.5,
             color = model_col,
             shape = 21) +
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence interval 
  geom_ribbon(data = volume_ih_predictions,
              aes(x = x,
                  y = predicted,
                  ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              fill = model_col) +
  
  # plot the prediction line
  geom_line(data = volume_ih_predictions,
            aes(x = x,
                y = predicted),
            color = model_col,
            linewidth = 1) +
  
  # labels
  labs(x = "Herbarium volume (mL)",
       y = "Initial volume (mL)") +
  
  # controlling axes to make the plot look square
  # this makes it easier to see the difference between the model and the 1:1 line
  scale_x_continuous(breaks = seq(from = 0, to = 15, by = 2.5), 
                     limits = c(0, 15)) +
  scale_y_continuous(breaks = seq(from = 0, to = 15, by = 2.5), 
                     limits = c(0, 15))
volume_ih_plot


  #.Scatterplot of vol_h(x) as Predictor of vol_i(y) with a species facet.
volume_ih_plot_species <- ggplot() +
  
  geom_point(data = volume_all,
             aes(x = vol_h,
                 y = vol_i,
                 color = species),
             alpha = 0.5,
             shape = 21) + 
  
  # plot a 1:1 reference line
  geom_abline(slope = 1, 
              intercept = 0,
              linetype = 2,
              linewidth = 1,
              color = ref_line_col) +
  
  # plot the confidence intervals
  geom_ribbon(data = volume_ih_predictions_species,
            aes(x = x,
                y = predicted,
                ymin = conf.low,
                ymax = conf.high,
                fill = species,
                group = species),
            alpha = 0.2) +
  
  # plot the model predictions
  geom_line(data = volume_ih_predictions_species,
            aes(x = x,
                y = predicted,
                color = species,
                group = species)) +
  
  # labels
  labs(x = "Herbarium volume (mL)",
       y = "Initial volume (mL)") +
  
  # theme
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text = element_text(size = 12)) +
  
  # facet
  facet_wrap(~ species, nrow = 2,
             scales = "free")


  volume_ih_plot_species

```


     #              Visualizing Rehydrate Summary Graphs           ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ 

```{r fig.width = 20, fig.height = 10}
# surf_ir_predictions, perimeter_ir_predictions, tdmc_ir_predictions, height_ir_predictions, width_ir_predictions, thick_ir_predictions, volume_ir_predictions



     #.........................Data Wrangling.........................

#creating a list of all the predictions for rehydrate traits
init_rehy_df <- rbind(surf_ir_predictions, # rbind stacks data frames on top of each other if they have the same columns
                      perimeter_ir_predictions, 
                      tdmc_ir_predictions, 
                      height_ir_predictions, 
                      width_ir_predictions, 
                      thick_ir_predictions, 
                      volume_ir_predictions) %>% 
  drop_na() # not sure why there are NA rows at the end of the data frame, but they come from one of the prediction data frames


     #.........A scatterplot with all seven model predictions.........
ggplot(data = init_rehy_df, # using the data frame created above
       aes(x = x, # x-axis
           y = predicted )) + # y-axis
  geom_abline(slope = 1, # adding a dashed grey 1:1 reference line
              intercept = 0,
              color = "grey",
              linetype = 2) + 
  # geom_ribbon(aes(fill = trait, # adding 95% CI 
  #                 ymin = conf.low,
  #                 ymax = conf.high),
  #             alpha = 0.2) +
  geom_line(aes(color = trait), 
            linewidth = 1) + # plotting model predictions
  labs(x = "Rehydrated value", # renaming the axes
       y = "Initial value") +
  theme(legend.position = "none") +
  facet_wrap(~trait, scales = "free")



```


     #  Creating a scatterplot that highlights 1:1 relationships   ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

```{r}
     #..............................Setup.............................

#Using the dataframe with all our rehydrate trait predictions to assign an opacity
#value to all traits. 3 signifies a close 1:1 relationship while 0.1 is a weak 1:1.

init23 <- init[init$trait != "thallus dry matter content"]
init23$opacity <- ifelse(init23$trait == "height", 3,
                      ifelse(init23$trait == "width", 3,
                             ifelse(init23$trait == "perimeter", 0.1, 
                                    ifelse(init23$trait == "surface area", 0.1, 
                                                  ifelse(init23$trait == "thickness", 0.1, 
                                                         ifelse(init23$trait == "volume", 0.1, NA ))))))
     #........manually offsetting height and width line labels........
label_df <- init23 %>% 
  filter(x == max(x)) %>% 
  mutate(label = stringr::str_to_title(trait),
         nudge_y = case_when(
           trait == "height" ~ 0.7,
           trait == "width" ~ -0.3,
           TRUE ~ 0
         ))

     #........................generating titles.......................
title <- "Two predictive trait models based on rehydrated values closely follow a 1:1 relationship"
subtitle <- "The traits that follow this pattern are Height and Width"

     #..............assigning each trait a unique color...............
showtext_auto()
trait_palette <- c("surface area" = "#ffbf00", 
                   "perimeter" = "#be8333", 
                  # "thallus dry matter content" = "#54662c", 
                   "height" = "#009bb0", 
                   "width" = "#124c54", 
                   "thickness" = "#368000", 
                   "volume" = "#b4450e")

     #........scatterplot with all rehydrate trait predictions........
     #......rehydrated trait value (x) & initial trait values (y).....
     #..excludes tdmc, and highlights traits with 1:1 relationships...
 plot_ir_1s <- init23 %>% 
  ggplot(aes(x, predicted, color = trait, alpha = opacity))+
  geom_line()+
  geom_abline(slope = 1, # adding a dashed grey 1:1 reference line
              intercept = 0,
              color = "grey",
              linetype = 2) + 
  # geom_ribbon(aes(fill = trait, # adding 95% CI (uncomment this if you want to see it)
  #                 ymin = conf.low,
  #                 ymax = conf.high),
  #             alpha = 0.2) +
  geom_line(
            linewidth = 0.5) + # plotting model predictions
  labs(x = "Rehydrated Value", # renaming the axes
       y = "Predicted Initial Value", 
       title = title,
       subtitle = subtitle) +
  scale_color_manual(values = trait_palette)+ #assigning values a color based on trait from our palette
  theme(legend.position = "none", 
        plot.background = element_blank())+
 #formatting line labels
    geom_text(
    data = init23 %>% filter(x == max(x)) %>% mutate(label = stringr::str_to_title(trait)),
    aes(label = label, alpha = opacity), 
    hjust = 0, 
    nudge_x = 0.1,
    nudge_y = label_df$nudge_y,
    size = 5, 
    family = "lex", 
    #alpha = opacity
    #fontface = "light"
  )+
   #formatting text and margins
  coord_cartesian(xlim = c(0, 7.2), 
                  clip = "off")+
  theme(plot.margin = margin(t = 1, r = 1, b = 1, l = 1, "cm"))+
   theme(axis.title.x = element_text(family = "lex",
                                 size = 14,
                                 hjust = 0.5,
                                 margin = margin(t = 0, r = 0, b = 0.5, l = 0, "cm")),
         axis.title.y = element_text(family = "lex",
                                 size = 14,
                                 hjust = 0.5,
                                 margin = margin(t = 0, r = 0, b = 0.5, l = 0, "cm")), 
          plot.title = element_text(family = "lex", 
                              size = 17, 
                              hjust = 0.5,
                              margin = margin(t = 0, r = 1, b = 0.3, l = 0, "cm")),
    plot.subtitle = element_text(family = "lex",
                                 size = 15,
                                 hjust = 0.5,
                                 margin = margin(t = 0, r = 0, b = 0.5, l = 0, "cm")))+
  scale_x_continuous(expand = c(0, NA))+
  scale_y_continuous(limits = c(0.8,NA))
 
 plot_ir_1s

```

     # A scatterplot highlighting relationships that deviate from 1:1 ~~~
     #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r fig.width = 10, fig.height = 10}

#.........................assigning opacity values (manually).........................

#traits that follow a 1:1 relationship are assigned 1, while deviants from 1:1
#are assigned 3. 
showtext_auto()
init <- init_rehy_df 
init2 <- as.data.frame(init) %>% 
  mutate(trait = as.factor(trait))

init2 <- init[init$trait != "thallus dry matter content"]
init2$opacity <- ifelse(init2$trait == "height", 1,
                      ifelse(init2$trait == "width", 1,
                             ifelse(init2$trait == "perimeter", 3, 
                                    ifelse(init2$trait == "surface area", 3, 
                                                  ifelse(init2$trait == "thickness", 1, 
                                                         ifelse(init2$trait == "volume", 3, NA ))))))

#.........................titles and palettes.........................

title <- "Predictive models based on rehydrated measurements vary by trait"
subtitle <- "The traits that deviate the most are Perimeter, Volume, and Surface Area"

showtext_auto()
trait_palette <- c("surface area" = "#ffbf00", 
                   "perimeter" = "#be8333", 
                  # "thallus dry matter content" = "#54662c", 
                   "height" = "#009bb0", 
                   "width" = "#124c54", 
                   "thickness" = "#368000", 
                   "volume" = "#b4450e")

#.........................plotting.........................
#......rehydrate trait values (x) & initial trait values (y).....

plot_ir_deviants <- init2 %>% 
  ggplot(aes(x, predicted, color = trait, alpha = opacity))+
  geom_line()+
  geom_abline(slope = 1, # adding a dashed grey 1:1 reference line
              intercept = 0,
              color = "grey",
              linetype = 2) + 
  # geom_ribbon(aes(fill = trait, # adding 95% CI (uncomment this if you want to see it)
  #                 ymin = conf.low,
  #                 ymax = conf.high),
  #             alpha = 0.2) +
  geom_line(
            linewidth = 1.5) + # plotting model predictions
  labs(x = "Rehydrated Value", # renaming the axes
       y = "Predicted Initial Value", 
       title = title,
       subtitle = subtitle) +
  scale_color_manual(values = trait_palette)+ #assigning palette colors to traits
  theme(legend.position = "none", 
        plot.background = element_blank())+
  geom_text( #formatting model labels
    data = init2 %>% filter(x == max(x)) %>% mutate(label = stringr::str_to_title(trait)),
    aes(label = label), 
    hjust = 0, 
    nudge_x = 0.1, 
    size = 5, 
    family = "lex"
    #fontface = "light"
  )+
  #manually adjusting text elements and plot dimensions
  coord_cartesian(xlim = c(0, 7.2), 
                  clip = "off")+
  theme(plot.margin = margin(t = 1, r = 1, b = 1, l = 1, "cm"))+
   theme(axis.title.x = element_text(family = "lex",
                                 size = 14,
                                 hjust = 0.5,
                                 margin = margin(t = 0, r = 0, b = 0.5, l = 0, "cm")),
         axis.title.y = element_text(family = "lex",
                                 size = 14,
                                 hjust = 0.5,
                                 margin = margin(t = 0, r = 0, b = 0.5, l = 0, "cm")), 
          plot.title = element_text(family = "lex", 
                              size = 17, 
                              hjust = 0.5,
                              margin = margin(t = 0, r = 0, b = 0.3, l = 0, "cm")),
    plot.subtitle = element_text(family = "lex",
                                 size = 15,
                                 hjust = 0.5,
                                 margin = margin(t = 0, r = 0, b = 0.5, l = 0, "cm")))+
  scale_x_continuous(expand = c(0, NA))+
  scale_y_continuous(limits = c(0.8,NA))

plot_ir_deviants
```

##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
##                        Miscellaneous/Outdated Code                       ----
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r fig.width = 20, fig.height = 10}

init_rehy_df <- rbind(surf_ir_predictions, # rbind stacks data frames on top of each other if they have the same columns
                      perimeter_ir_predictions, 
                      tdmc_ir_predictions, 
                      height_ir_predictions, 
                      width_ir_predictions, 
                      thick_ir_predictions, 
                      volume_ir_predictions) %>% 
  drop_na() # not sure why there are NA rows at the end of the data frame, but they come from one of the prediction data frames

ggplot(data = init_rehy_df, # using the data frame created above
       aes(x = x, # x-axis
           y = predicted, 
           color = trait)) + # y-axis
  geom_abline(slope = 1, # adding a dashed grey 1:1 reference line
              intercept = 0,
              color = "grey",
              linetype = 2) + 
  # geom_ribbon(aes(fill = trait, # adding 95% CI (uncomment this if you want to see it)
  #                 ymin = conf.low,
  #                 ymax = conf.high),
  #             alpha = 0.2) +
  geom_line( 
            linewidth = 1) + # plotting model predictions
  labs(x = "Rehydrated value", # renaming the axes
       y = "Initial value") +
  theme(legend.position = "none") +
  facet_wrap(~trait, scales = "free")
```

#Visualize the linear model I & Rehydrate
```{r}
#Height

ggpredict(height_reg_ir, terms = c("height_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Width
ggpredict(width_reg_ir, terms = c("width_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Perimeter
ggpredict(perimeter_reg_ir, terms = c("per_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Surface Area
ggpredict(surf_reg_ir, terms = c("surf_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#TDMC
ggpredict(tdmc_reg_ir, terms = c("weight_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Thickness
ggpredict(thick_reg_ir, terms = c("thick_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Volume
ggpredict(volume_reg_ir, terms = c("vol_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

```




#Create multiple regression for each trait initial & herbarium
```{r}
#Height
height_reg_ih <- lmer(height_i ~ height_h * species + (1 | individual_id), data = height_all)
summary(height_reg_ih)

#Width
width_reg_ih <- lmer(width_i ~ width_h * species + (1 | individual_id), data = width_all)
summary(width_reg_ih)

#Perimeter
perimeter_reg_ih <- lmer(per_i ~ per_h * species + (1 | individual_id), data = perimeter_all)
summary(perimeter_reg_ih)

#Surface Area
surf_reg_ih <- lmer(surf_i ~ surf_h * species + (1 | individual_id), data = surf_all)
summary(surf_reg_ih)

#TDMC
tdmc_reg_ih <- lmer(weight_i ~ weight_h * species + (1 | individual_id), data = tdmc_all)
summary(tdmc_reg_ih)

#Thickness
thick_reg_ih <- lmer(thick_i ~ thick_h * species + (1 | individual_id), data = thickness_all)
summary(thick_reg_ih)

#Volume
volume_reg_ih <- lmer(vol_i ~ vol_h * species + (1 | individual_id), data = volume_all)
summary(volume_reg_ih)

```




#Visualize the linear models I & Herbarium
```{r}
#Height

ggpredict(height_reg_ih, terms = c("height_h", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "red"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "red"))

#Width
ggpredict(width_reg_ih, terms = c("width_h", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Perimeter
ggpredict(perimeter_reg_ih, terms = c("per_h", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Surface Area
ggpredict(surf_reg_ih, terms = c("surf_h", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#TDMC
ggpredict(tdmc_reg_ih, terms = c("weight_h", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Thickness
ggpredict(thick_reg_ir, terms = c("thick_r", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Volume
ggpredict(volume_reg_ih, terms = c("vol_h", "species")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

```




#Summary graphs
```{r}
#Add 1:1 Line (I couldn't figure this out!)
#https://stackoverflow.com/questions/75101739/add-horizontal-line-to-an-effects-plot-with-different-intercepts-per-panel

#graphs without species lines
#Does this incorporate individual effects?
#height IR
ggpredict(height_reg_ir, terms = "height_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Width IR
ggpredict(width_reg_ir, terms ="width_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Perimeter IR
ggpredict(perimeter_reg_ir, terms = "per_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Surface Area IR
ggpredict(surf_reg_ir, terms = "surf_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#TDMC IR
ggpredict(tdmc_reg_ir, terms = "weight_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Thickness IR
ggpredict(thick_reg_ir, terms = "thick_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Volume IR
ggpredict(volume_reg_ir, terms = "vol_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#####IH GRAPHS Species not displayed

#height IH
ggpredict(height_reg_ih, terms = ("height_h")) %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "red"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "red"))

#Width
ggpredict(width_reg_ih, terms ="width_h") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Perimeter
ggpredict(perimeter_reg_ih, terms = "per_h") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Surface Area
ggpredict(surf_reg_ih, terms = "surf_h") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#TDMC
ggpredict(tdmc_reg_ih, terms = "weight_h") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Thickness
ggpredict(thick_reg_ir, terms = "thick_r") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#Volume
ggpredict(volume_reg_ih, terms = "vol_h") %>% 
 plot(show_data=TRUE) +
scale_color_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("white", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

#graph with facet species
ggpredict(height_reg_ir, terms = c("height_r", "species")) %>% 
 plot(show_data=TRUE, facet = TRUE) +
scale_color_manual(values = c("black", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))+
 scale_fill_manual(values = c("black", "burlywood4", "antiquewhite", "azure3", "cornflowerblue", "cornsilk3", "blue4", "burlywood3", "darkgoldenrod3", "brown3", "brown", "black", "black"))

```





